---
title: "CMDA 3654 Assignment 4"
author: "Chase Sinclair"
date: "3/30/2020"
output: html_document
---
Honor code: 

The Virginia Tech honor pledge for assignments is as follows:
“I have neither given nor received unauthorized assistance on this assignment.”
-CHASE

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load "mtcars" dataset
```{r load}
data("mtcars")
```

## Problem 1
### Part A
```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, col = factor(cyl))) + 
  geom_point()
```

From the plot of mpg vs hp, we can see that gross horsepower increases when the number of cylinders increase. An automobile with 4 cylinders will have the least hp contrary to a automobile with 8 cylinders with the highest hp. We can also see that mpg is the highest when the automobile has less cylinders in it. So the mpg of a car will go down as you increase the amount of cylinders in it. 

### Part B

When transmission is __automatic__ it is labled (0) and when the transmission is __manual__ it is labled (1).

### Part C
```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, wt, col = factor(am))) + 
  geom_point()
```

From the plot, I think automatic and manual transmission can be distinguished by weight, but not hp. From the plot, we observe that automatic transmissions tend to have higher weight than transmissions that are manual. However, from the plot, we can not observe that the type of transmission is influenced by hp. We will calculate this relationship in our models later on.

### Part C
```{r}
fit1 = glm(am~wt,data=mtcars,family = "binomial")
summary(fit1)
```

Let's interpret this model. The coefficient for wt is a small negative number, and the p-value is less than 5% which implies that wt is a significant feature. Recall that the plot of wt vs am showed a difference between the weight of automatic vs manual transmissions. So this tells us that our visual interpretation was right. Weight is a significant predictor of default. 

Heavier cars are less likely to have manual transmission.

Since the coefficient is negative, the odds ratio goes down by exp(b) times when the weight increases by 1 unit (1000 lbs).

Thus, when weight increases by 1000 lbs, the odds of having the manual transmission goes down 0.0178 times. 

### Part D
```{r}
fit2 = glm(am~hp,data=mtcars,family = "binomial")
summary(fit2)
```

Accrding to our summary with hp as the only feature to the model, it does not fit the model because it is not significant as it has a p-value greater than 5%. So, using this model we cannot explain whether cars with higher horsepower are more likely or less likely to have manual transmission. However we can still make estimations from it. 

Since the coefficient is negative b = -0.008117, the odds ratio goes down by exp(b) times when the hp increases by 1 unit. So the odds ratio goes down 0.9919 when the hp increases by 1.

Thus, when hp increases by 100, the odds of having the manual transmission goes down exp(100b)

If horsepower increases by 100, the change in odds of a car having manual transmission goes down by 0.4441.

### Part F

If I had to choose between these two models, I would choose the model with wt as the feature. This model is better because wt is significant in the model, unlike hp in the second model, and has a lower AIC score at 23.176 where the second model has a worse AIC score of 45.228. 
